Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-11-26 ICLR25/proofsb.tex
update

\begin{figure}[t!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
	\caption{Time and uncertainty scaling of table \ref{table15}.
		Time is using logscale.}
	\label{fig3LP}
\end{figure}

@@

@@

\begin{figure}[t]\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer7_comparison.png}.
	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
	\label{fig4}
\end{figure}

@@

@@

\subsection{Table for Figure \ref{fig_table3}}

Finall, we provide the table corresponding to the Figure \ref{fig_table3}

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=55$}&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-7}
		\text{$|X|$}  & \text{Random} & Huang & \bf Utility& \text{Random} &BSR &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  &  1.761& 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729& 1.7138 &  \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & 1.6775& \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& 1.6392& \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 &1.5938 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 &1.5534 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & 1.5166& \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & 1.4788 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & 1.4395& \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

@@

\section{SR Heuristic for choosing nodes}

Here we provide the formula of BaB-SR from paper \cite{BaB}.

@@

>>>>

@@

\begin{figure}[b!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer3_comparison_LP}.
	\caption{Time and uncertainty scaling of table 7.
		Time is using logscale.}
	\label{fig3LP}
\end{figure}

@@

@@

\begin{figure}[h]\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Layer7_comparison.png}.
	\caption{Comparison of uncertainty at layer 7 for full MILP with different time-outs vs pMILP with different number of open nodes. Time is using logscale.}
	\label{fig4}
\end{figure}

@@

@@

Here we cite the formula of BaBSR from paper \cite{BaB}.

@@

\begin{figure}[b!]
	\hspace*{-0.8cm}
	\includegraphics[scale=0.6]{Plot for table 3}.
	\caption{Plot for table 3}
	\label{fig_table3}
\end{figure}

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|}
		\hline
		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
		5  & 1.729& 1.7138 &  &\bf 1.532 \\ \hline
		10  & 1.696 & 1.6775& &\bf  1.371\\ \hline
		15  &   1.653& 1.6392& &\bf  1.247\\ \hline
		20  &   1.619 &1.5938 & &\bf  1.145\\ \hline
		25  &    1.586 &1.5534 & &\bf 1.061\\ \hline
		30  &  1.546 & 1.5166& &\bf  0.989 \\ \hline
		35  &   1.502 & 1.4788 & &\bf 0.934 \\ \hline
		40  &  1.469 & 1.4395& &\bf 0.921 \\ \hline \hline
		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
	\end{tabular}
	\caption{BSR and FSB}
	\label{BSRandFSB}
	%\vspace{-0.6cm}
\end{table}
